---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.




# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

  
  The trend for males appears to be going upward through the graph as they think its okay, while in opposition females appear to be going downward; projecting that they don't think its okay.  
  
```{r}
rowPerc(xsex_sex)
colPerc(xsex_sex)
```
  
In row percent, males appear to be getting larger as you go from wrong to okay, while females appear to be getting smaller.   

```{r}
chisqtestGC(xsex_sex,graph=TRUE)
```
  
  The p-value of 0.0351 is low, therefore indicating if the null hypothesis was true we would get it 35 times out of 1000. We then choose to reject the null hypothesis.  

#Polyview

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

#Relationship Status




# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
