---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.




# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

  
  The trend for males appears to be going upward through the graph as they think its okay, while in opposition females appear to be going downward; projecting that they don't think its okay.  
  
```{r}
rowPerc(xsex_sex)
colPerc(xsex_sex)
```
  
In row percent, males appear to be getting larger as you go from wrong to okay, while females appear to be getting smaller.   

```{r}
chisqtestGC(xsex_sex,graph=TRUE)
```
  
  The p-value of 0.0351 is low, therefore indicating if the null hypothesis was true we would get it 35 times out of 1000. We then choose to reject the null hypothesis.  

#Polyview

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
source("makeTables2016.R")
barchartGC(xsex_polv,type="percent")
```
  
According to the barchart, liberals are most comfortable with sex while conservatives are least comfortable with sex, seen with the striking numerical difference.
  
```{r}
rowPerc(xsex_polv)
colPerc(xsex_polv)
```
  
  Liberals who think its wrong start low and increase, but then they start to decrease again. However, moderates appear to start high then level out across hmm to okay. Lastly, conservatives appear to follow the trend as they start high, level out from hmm to okay. This shows the similarities in moderate to conservatives, while the liberals go in the opposite direction.  
  
```{r}
chisqtestGC(xsex_polv,graph=TRUE)
```
    
    
  With the extremely low p-value, it is easy to note the chances of this rarely occurring. This helps us choose to reject the null hypothesis.

#Relationship Status




# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
