---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.




# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->



#Polyview

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

#Relationship Status
```{r}
source("makeTables2016.R")
barchartGC(xmsex_table,type="percent")
```
   
  In the above graph, we can see in the column titled "hooked up" that it is going downward on the graph. While on the other hand, the column titled "single" appears to be going upward.  
  
```{r}
colPerc(xmsex_table)
rowPerc(xmsex_table)
```
  
  The trend is smaller for people in a relationship as we go across, while its bigger for those single as we go from wrong to okay.  
    
```{r}
chisqtestGC(xmsex_table,graph=TRUE,simulate.p.value = TRUE)
``` 
  
  This says that if the null hypothesis was true, it would happen only 7 1/2 out of a thousand, therefore we choose to reject the null hypothesis using the evidence. 
  

  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
